\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{array}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{setspace}

\hypersetup{
  colorlinks=true,
  urlcolor=blue,
  linkcolor=black
}

\setlist[itemize]{leftmargin=*,topsep=2pt,itemsep=2pt,parsep=0pt}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}

\titleformat{\section}{\large\bfseries}{\thesection}{0.5em}{}
\titlespacing*{\section}{0pt}{8pt}{4pt}

\begin{document}

{\huge \textbf{M Shafri Syamsuddin}}\\[2pt]
\begin{tabularx}{\textwidth}{@{}X X@{}}
Semarang, Indonesia 50273 & \href{mailto:shafrisyamsuddin@gmail.com}{shafrisyamsuddin@gmail.com}\\
\href{tel:+6283137190178}{+62 831 3719 0178} & \href{https://www.linkedin.com/in/shafrisyamsuddin/}{linkedin.com/in/shafrisyamsuddin} \\
\href{https://github.com/Shafriii}{github.com/Shafriii} &
\end{tabularx}

\section*{Summary}
Computer vision and NLP engineer translating research-grade models into deployable products. Experience building YOLO-based malaria diagnostics, zero-shot sentiment analytics, and Docker-first inference services. Comfortable driving projects end-to-end: data strategy, modelling, MLOps, and stakeholder alignment.

\section*{Experience}
\textbf{CEO \& Product Lead} \hfill Jun 2022 -- Dec 2023\\
JIWANA (Startup at UBIC Incubation), Yogyakarta, ID
\begin{itemize}
  \item Represented the mental-health chatbot startup across incubation events, forging partnerships and securing mentorship support.
  \item Directed product roadmap and team coordination, translating user research into actionable requirements.
  \item Co-designed conversational flows and spearheaded prototype experimentation to validate technical feasibility.
\end{itemize}

\textbf{Data Scientist Trainee} \hfill Oct 2024 -- Mar 2025\\
Rakamin Academy, Remote
\begin{itemize}
  \item Completed intensive programme covering DBMS, SQL, Python (NumPy, pandas), statistics, scikit-learn, classical ML, ensemble methods, and deep learning.
  \item Delivered an automated CV summarisation pipeline using NLP techniques to evaluate applicants on academic, social, and professional criteria.
  \item Practised end-to-end MLOps fundamentals: experiment tracking, evaluation, and deployment-readiness documentation.
\end{itemize}

\textbf{Human Resource Development Staff} \hfill Sep 2020 -- Jun 2022\\
Ikatan Mahasiswa Indonesia Xiaozhuang (IMIX), Yogyakarta, ID
\begin{itemize}
  \item Designed and delivered capability-building programmes covering technical and soft skills for student members.
  \item Managed performance assessments, feedback loops, and events to sustain an inclusive, high-performing community.
\end{itemize}

\section*{Selected Projects}
\textbf{Malaria Parasite Stage Detection} \hfill 2024 -- Present
\begin{itemize}
  \item Master thesis project creating assistive lab tooling with YOLOv8 \& Faster R-CNN ensembles enhanced by LAB colour-space feature insertion.
  \item Improved mAP\textsubscript{50} from 0.61 (RGB baseline) to 0.69, supporting species \& life-stage detection for Plasmodium falciparum, vivax, malariae, and ovale.
  \item Exported models to ONNX and wrapped inference in a lightweight executable for deployment in clinics without Python stacks.
\end{itemize}

\textbf{VisionServe: CIFAR-10 Inference API} \hfill 2025
\begin{itemize}
  \item Dockerised FastAPI microservice serving CNN predictions with reproducible training pipelines and artifact versioning.
  \item Implemented single-command automation for preprocessing, training, metrics export, and QA artefacts (confusion matrix, history).
  \item Calibrated predictions with probability distributions and mounted model artefacts at runtime for lean deployment.
\end{itemize}

\textbf{Zero-shot Sentiment Intelligence Pipeline} \hfill 2025
\begin{itemize}
  \item Config-driven orchestration using \texttt{facebook/bart-large-mnli} to score public comments without domain-specific fine-tuning.
  \item Generated dashboards-ready outputs: sentiment trendlines, label share analyses, and confidence diagnostics.
  \item Structured pipeline for rapid migration into APIs or scheduled batch processing with minimal refactoring.
\end{itemize}

\section*{Education}
\textbf{Universitas Gadjah Mada} \hfill Aug 2023 -- Jul 2025\\
Master of Computer Science (GPA 3.73/4.00) \\
Thesis: Feature Insertion and Colour Space Transformation for Malaria Parasite Detection in Thin Blood Smear Images using YOLO \& Faster R-CNN.\\
\begin{itemize}
  \item Built research publication trend warehouse from Springer metadata to surface emerging topics with advanced visual analytics.
  \item Led hotel price trend mining across Booking.com, Traveloka, and Tiket.com via Octoparse; analysed pricing vs. city-centre proximity.
\end{itemize}

\textbf{Nanjing Xiaozhuang University (NXU)} \hfill 2020 -- 2021\\
Double Degree Programme, Information Engineering\\
Completed cross-cultural coursework in systems engineering, algorithms, and applied research collaboration.

\textbf{Universitas Islam Indonesia} \hfill Sep 2018 -- Jun 2022\\
Bachelor of Computer Science (GPA 3.68/4.00)\\
Undergraduate thesis: Developed a serious game that teaches algorithmic thinking for secondary education.

\section*{Publications}
Syamsuddin, M. S., et al. \textit{Exploring the Impact of Colour Space in Malaria Parasite Detection using Deep Learning}. AMLDS 2025, Tokyo, Japan. Published by IEEE Xplore. \href{https://ieeexplore.ieee.org/document/11159455}{https://ieeexplore.ieee.org/document/11159455}

\section*{Certifications \& Scores}
\begin{itemize}
  \item TOEFL ITP -- Score: 637 (ITC, Mar 2025)
  \item TPA Online -- Score: 591 (Pusat Layanan Tes Indonesia, Jun 2025)
  \item Data Scientist Programme, Rakamin Academy -- Completed Oct 2024 to Mar 2025
\end{itemize}

\section*{Technical Skills}
\textbf{Programming \& ML:} Python, PyTorch, TensorFlow, Keras, scikit-learn, YOLOv8, OpenCV, ONNX\\
\textbf{NLP \& Analytics:} Hugging Face Transformers, Zero-shot Learning, SQL, PostgreSQL, Power BI, Tableau, Plotly, Streamlit\\
\textbf{MLOps \& Deployment:} FastAPI, Flask, Docker, MLflow, GitHub Actions, Apache Airflow\\
\textbf{Tools:} Unity, Figma, Git

\end{document}
